Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-08-25 group-c/E3-calibration-figure.Rmd
update calibration figure to include validation points

colnames(calibration_points) <- c("x","y")

df <- as_tibble(calibration_points)
```

```{r echo=FALSE, fig.cap="Calibration point locations for Experiment 3."}
ggplot(df, aes(x=x, y=y))+
  geom_point(size=3)+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  theme(panel.border = element_rect(color="black", fill=NA))
```

>>>>

validation_points <- matrix(c(
  c(10,50),
  c(50,50),
  c(90,50)
), ncol=2, byrow=T)

colnames(calibration_points) <- c("x","y")
colnames(validation_points) <- c("x","y")

df <- as_tibble(calibration_points) %>% bind_rows(as_tibble(validation_points))
df$point <- c(rep("calibration", nrow(calibration_points)), rep("validation", nrow(validation_points)))
```

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2022-08-25 manuscript.tex
update calibration figure to include validation points

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
  pdfauthor={Joshua R. de Leeuw1, Rachel Ryskin2, Ariel N. James3, Joshua K. Hartshorne4, Haylee Backs1, Nandeeta Bala1, Laila Barcenas-Meade1, Samata Bhattarai1, Tessa Charles1, Gerasimos Copoulos1, Claire Coss1, Alexander Eisert1, Elena Furuhashi1, Keara Ginell1, Anna Guttman-McCabe1, Emma (Chaz) Harrison1, Laura Hoban1, William A. Hwang1, Claire Iannetta1, Kristen M. Koenig1, Chauncey Lo1, Victoria Palone1, Gina Pepitone1, Margaret Ritzau1, Yi Hua Sung1, \& Lauren Thompson1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

The third study was a replication attempt of
Manns, Stark, and Squire (2000) which aimed to show that the visual
paired-comparison task, widely used in the patient literature, tapped
into declarative memory. In the visual paired-comparison task, two
identical pictures were presented side by side for a brief viewing
period. After a delay, one of the previously viewed pictures was
presented along with a new picture. Individuals looked more at the new
picture than the old picture and the time spent looking was correlated
with later recognition memory performance. On the other hand perceptual
priming, thought to recruit non-declarative memory, was not linked to
later recognition. (The perceptual priming arm of the design was not
included in this replication.)

@@

@@

Our initial sample size was 51 participants for the first day of our
experiment and 48 of them came back for the second day. Following Manns
et al., we excluded 3 participants due to perfect performance on the
recognition memory test. Our final sample size was 45 participants.

@@

The task began with a 7-point eye-tracker calibration (each point was
presented 3 times in a random order) and validation with 3 points (each
presented once). The point locations were designed to focus calibration
on the center of the screen and the middle of the left and right halves
of the screen. The experiment was administered over the course of two
consecutive days. It consisted of three sections: a presentation phase,
a test phase, and a recognition test. The first two phases occurred on
the first day, while the recognition test occurred on the second day.

@@

Approximately 24 hours after completing the first session, with a leeway
interval of 12 hours to accommodate busy schedules, participants were
given the recognition test. It consisted of 48 photographs, presented
one at a time. Each was shown on the screen for 1 second, followed by a
1 second interstimulus interval. Half of the pohotographs had been
viewed twice on the previous day and were deemed the ``targets.'' The
other half depicted an object with the same name as an object in one of
the old photographs, but had not been viewed before, deemed ``foils.''
Each photograph remained on the screen until the participants indicated
whether or not they had seen it before by pressing `y' for yes and `n'
for no. After they pressed one of the two keys, a prompt on the screen
asked them to rate their confidence in their answer from 1 as a ``pure
guess'' to 5 as ``very sure.'' by clicking on the corresponding number on
the screen. No feedback on their responses was given during the test.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Eye-tracking on the web: lessons learned from replicating 5 experiments},
  pdfauthor={Joshua R. de Leeuw1, Rachel Ryskin2, Ariel N. James3, Joshua K. Hartshorne4, Haylee Backs1, Nandeeta Bala1, Laila Barcenas-Meade1, Samata Bhattarai1, Tessa Charles1, Gerasimos Copoulos1, Claire Coss1, Alexander Eisert1, Elena Furuhashi1, Keara Ginell1, Anna Guttman-McCabe1, Emma (Chaz) Harrison1, Laura Hoban1, William A. Hwang1, Claire Iannetta1, Kristen M. Koenig1, Chauncey Lo1, Victoria Palone1, Gina Pepitone1, Margaret Ritzau1, Yi Hua Sung1, \& Lauren Thompson1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

The third study was a partial replication attempt of
Manns, Stark, and Squire (2000). This experiment used the visual
paired-comparison, which involves presenting a previously-viewed image
and novel image together and measuring the proportion of time spent
looking at each image. The expected pattern of results is that
participants will look more at novel objects. They
Manns et al. (2000) hypothesized that this pattern of
behavior could be used to measure the strength of memories. If a viewer
has a weak memory of the old image, then they may look at the old and
new images roughly the same amount of time. They tested this in two
ways. First, they showed participants a set of images, waited five
minutes, and then paired those images with novel images. They found that
participants spent more time (58.8\% of total time) looking at the novel
images. They then measured memory performance one day later and found
that participants were more likely to recall images that they had spent
less time looking at during the visual paired-comparison task the
previous day.

@@

The stimuli, experimental code, and data and analysis scripts can be
found on the Open Science Framework at \url{https://osf.io/k63b9/}
(\url{https://osf.io/k63b9/}). The pre-registration for the study can be
found at \url{https://osf.io/48jsv} (\url{https://osf.io/48jsv}). We
inadvertently did not create a formal pre-registration using the OSF
registries tool, but this document contains the same information and is
time stamped prior to the start of data collection.

@@

Our pre-registered target was 50 participants. 51 participants completed
the first day of the experiment and 48 completed the second day.
Following Manns et al., we excluded 3 participants due to perfect
performance on the recognition memory test because this prevents
comparison of gaze data for recalled vs.~non-recalled images. Our final
sample size was 45 participants.

@@

The task began with a 7-point eye-tracker calibration (each point was
presented 3 times in a random order) and validation with 3 points (each
presented once). The point locations were designed to focus calibration
on the center of the screen and the middle of the left and right halves
of the screen.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-36-1.pdf}
\caption{\label{fig:unnamed-chunk-36}Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.}
\end{figure}

The experiment was administered over the course of two
consecutive days. It consisted of three sections: a presentation phase,
a test phase, and a recognition test. The first two phases occurred on
the first day, while the recognition test occurred on the second day.

@@

Approximately 24 hours after completing the first session, with a leeway
interval of 12 hours to accommodate busy schedules, participants were
given the recognition test. It consisted of 48 photographs, presented
one at a time. Each was shown on the screen for 1 second, followed by a
1 second interstimulus interval. Half of the photographs had been
viewed twice on the previous day and were deemed the ``targets.'' The
other half depicted an object with the same name as an object in one of
the old photographs, but had not been viewed before, deemed ``foils.''
Each photograph remained on the screen until the participants indicated
whether or not they had seen it before by pressing `y' for yes and `n'
for no. After they pressed one of the two keys, a prompt on the screen
asked them to rate their confidence in their answer from 1 as a ``pure
guess'' to 5 as ``very sure.'' by clicking on the corresponding number on
the screen. No feedback on their responses was given during the test.
